### 2014-01-07 disc_arfi_mr.tex

We did not expect perfect agreement between MR and ARFI imaging by volume or tri-axial
 dimensions since each modality applies a different amount of external compression to 
the rectal wall that deforms the prostate different amounts. Pressure on the prostate 
during ARFI imaging is modulated by the urologist when he locks the transducer rotation 
apparatus in place prior to imaging, and deformation of the prostate can be easily visualized
 during this alignment process.  It was our goal to apply as little pressure while still maintaining
 uniform contact throughout the image acquisition. This is critical since poor acoustic coupling to 
the prostate through the rectal wall can greatly diminish ARFI image displacement SNR.

>>>>

We did not expect perfect agreement between MR and ARFI imaging volume or tri-axial
 dimensions since each modality applies a different amount of external compression to 
the rectal wall that deforms the prostate different amounts. Pressure on the prostate 
during ARFI imaging is modulated by the urologist when he locks the transducer rotation 
apparatus in place prior to imaging, and deformation of the prostate can be easily visualized
 during this alignment process.  It was our goal to apply as little pressure while still maintaining
 uniform contact throughout the image acquisition. This is critical since poor acoustic coupling to 
the prostate through the rectal wall can greatly diminish ARFI image displacement SNR.
